Actuator line modeling of vertical-axis turbines

### 2016-04-28 paper.tex
Remove more template content

\section{The Three Golden Rules}

Before we proceed, we would like to stress \emph{three golden
rules} that need to be followed to enable the most efficient use
of your code at the typesetting stage:
\begin{enumerate}
\item[(i)] keep your own macros to an absolute minimum;

\item[(ii)] as \TeX\ is designed to make sensible spacing
decisions by itself, do \emph{not} use explicit horizontal or
vertical spacing commands, except in a few accepted (mostly
mathematical) situations, such as \verb"\," before a
differential~d, or \verb"\quad" to separate an equation from its
qualifier;

\item[(iii)] follow the \emph{\journalnamelc} reference style.
\end{enumerate}

\begin{table}
    \caption{This is a sample table}
    \centering
    \small
    \begin{tabular}{c|c|c}
    \toprule
    This & that & other\\
    \midrule
    yo & yo & yo\\
    \bottomrule
    \end{tabular}
\end{table}

@@

\bibliographystyle{wileyj.bst}
\bibliography{library}
\end{document}

>>>>

@@

\bibliographystyle{wileyj}
\bibliography{library}
\end{document}
